---
title: "Basic workflow using rocc"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{check}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::load_all()
library(knitr)
```

## 0. Installing and loading package

```{r eval = FALSE}
remotes::install_github("saramortara/rocc")
library(rocc)
```


## 1. Download and bind data from different sources

### Species Link

Here, we are downloading data from two species of ferns.

```{r rspecieslink}
species = c("Asplenium truncorum", "Lindsaea lancea")
data_splink <- rspeciesLink(species = species, 
                            filename = "specieslink")
```

### GBIF

```{r}
data_gbif <- rgbif2(species = species, 
                    filename = "gbif")
```

### Bind data from different sources


## 3. Check string in species name

Given that the data base might come from source with errors, we perform a basic check on the string of a species name. We will select only unique entries in species names.

```{r species-raw}
# Vector of unique entries in species names
species_name_raw <- unique(data_splink$data$scientificName) 
```

For the unique entries, we will perform a basic check on the string.

```{r check-string}
species_name_check  <- check_string(species_name_raw)
species_name_check
```

Here, we are interested only in the names assigned with `possibly_ok`. We see that names with `not_Genus_epithet_format` are probably variety and will be treated separately later.

Now getting only possible correct and unique names. 

```{r species-ok}
species_ok <- species_name_check[species_name_check$speciesStatus %in% "possibly_ok", ]
```

## 4. Taxonomic check

First, we will check for typos and get a list of possible names. 

```{r suggest}
suggest_taxa <- suggest_flora(species_ok$species)
search_taxa <- unique(suggest_taxa$species)
```


```{r check_taxon} 
list_taxa <- lapply(search_taxa, check_flora)
```

### Output

Still deciding the output. The columns `synonym` and `scientificName_search` were additioned by hand inside function, other columns are exactly the same as in the API of Brazilian Flora 2020. 

#### *Lindsaea lancea*

```{r lindsaea}
# L. lancea
list_taxa[[1]]$taxon
list_taxa[[1]]$synonyms
```

#### *Asplenium truncorum*

```{r asplenium}
# para A. truncorum
list_taxa[[2]]$taxon
list_taxa[[2]]$synonyms
```

