---
title: "Building an workflow of taxonomic check"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{check}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::load_all()
library(knitr)
```

## 0. Installing and loading package

```{r eval = FALSE}
remotes::install_github("saramortara/rocc")
library(rocc)
```


## 1. String check

The function `check_status` makes preliminary check in a scientific name, catching most common errors in species names such as:

- `not_Genus_epithet_format`: scientific name not following the expected pattern genus and epithet separated by space
- `variety`: species scientific name with variety
- `subspecies`: species scientific name with subspecies
- `conferre`: open nomenclature cf. in species scientific name
- `affinis`: open nomenclature aff. in species scientific name
- `name_w_authors`: species scientific name has authors
- `not_name_has_digits`: species scientific name has digits, not a valid name
- `indet`: species identified only at genus level
- `family_as_genus`: species family as genus, not a valid name
- `non_ascii`: species name has non ASCII characters, not a valid name
- `hybrid`: x
- `parasite`: f. sp. 



```{r check_status}
species <- c("Lindsaea lancea var. falcata", "Asplenium Aff. truncorum", 
             "Aspidosperma discolor", "Aspidosperma Discolor", 
             "Aspidosperma discolor A.DC.", "Aspidosperma cf. discolor", 
             "Aspidosperma CF. discolor", "Aspidosperma aff. discolor",
             "Aspidosperma Aff. discolor", "Aspidosperma sp. discolor", 
             "Aspidosperma cf.discolor", "Aspidosperma dicolor", 
             "Apocynaceae Aspidosperma", "Aspidosperma cf. discolor A.DC.", 
             "Aspidosperma aff. discolor A.DC.", "Aspidosperma discolor A. & DC.", 
             "Asplenium sp.", "Asplenium sp 2", 
             "Asplenium sp. nov. truncorum", "Asplenium truncorum 2", 
             "cf. Piper dilatatum", "Piper dilatatum sp. nov.", 
             "aff. Piper dilatatum", "Miconia albicans (Sw.) Triana", 
             "Miconia albicans (Sw.) TRIana", "Bowlesia incana f. crassifolia", 
             "Gleicheniales",  "incertae sedis", "Chamissoa acuminata Mart. var. acuminata", 
             "Entrophospora R.N. Ames & R.W. Schneid. 1979", "Schinopsis brasiliensis var. glabra Engl.", 
             "Peronospora hyoscyami f. sp. tabacina Skalický", "Bla bla Fulano f.", 
             "Syagrus ×andrequiceana", "Agalinis itambensisxangustifolia?", 
             "Byrsonima rich.", "Morganella rimosa Baseia & Alfredo sp. nov.", 
             "Leandra euphorbioides (Naudin) D`El Rei Souza & Baumgratz", 
             "Cyrtocymura harleyi (H.Rob.) H.Rob.", "S polyphylla", 
             "Phaseolus robustus Piper", "Catasetum ×splendens Cogn.", 
             "Catasetum ×evangelistae V.P.Castro & G.F.Carr", "Metrodorea mollis",
             "Salvinia ×delasotae C.V. Miranda & Schwartsb.", "Helietta glaziovii", 
             "Drosera ×fontinalis Rivadavia", "Diplazium lepthochlamys")

df <- check_string(species)
```

Checking the output of `check_string()`

```{r, echo = FALSE}
kable(df[order(df$scientificName_status, df$scientificName), ], row.names = FALSE)
```

Now getting only possible correct and unique names. 

```{r species_ok}
ok <- c("variety", 
        "possibly_ok", 
        "name_w_wrong_case",
        "name_w_authors")

df_ok <- df[df$scientificName_status %in% ok, ]

species_new <- unique(df_ok$scientificName_new)
```

## 2. Taxonomic check

First, we will check for typos and get a list of possible names. 

```{r suggest}
suggest_taxa <- suggest_bfg(species_new)
search_taxa <- na.omit(as.character(unique(suggest_taxa$scientificName_suggest)))
```


```{r check_taxon} 
list_taxa <- lapply(search_taxa, check_bfg)
```

### Output

Still deciding the output. The columns `synonym` and `scientificName_search` were additioned by hand inside function, other columns are exactly the same as in the API of Brazilian Flora 2020. 
#### *Lindsaea lancea*

```{r lindsaea}
# L. lancea
list_taxa[[1]]$taxon
list_taxa[[1]]$synonyms
```

#### *Aspidosperma discolor*

```{r aspidosperma}
# para A. discolor
list_taxa[[2]]$taxon
list_taxa[[2]]$synonyms
```

