---
title: "Previous taxonomic check"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{check}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::load_all()
```

## String check

The function `check_status` makes preliminary check in a scientific name, catching most common errors in species names such as:

- `not_Genus_epithet_format`: scientific name not following the expected pattern genus and epithet separated by space
- `variety`: species scientific name with variety
- `subspecies`: species scientific name with subspecies
- `conferre`: open nomenclature cf. in species scientific name
- `affinis`: open nomenclature aff. in species scientific name
- `name_w_authors`: species scientific name has authors
- `not_name_has_digits`: species scientific name has digits, not a valid name
- `indet`: species identified only at genus level
- `family_as_genus`: species family as genus, not a valid name
- `non_ascii`: species name has non ASCII characters, not a valid name


```{r}
species <- c("Lindsaea lancea var. falcata", "Asplenium Aff. truncorum", 
             "Aspidosperma discolor", "Aspidosperma Discolor", 
             "Aspidosperma discolor A.DC.", "Aspidosperma cf. discolor", 
             "Aspidosperma CF. discolor", "Aspidosperma aff. discolor",
             "Aspidosperma Aff. discolor", "Aspidosperma sp. discolor", 
             "Aspidosperma cf.discolor", "Aspidosperma dicolor", 
             "Apocynaceae Aspidosperma", "Aspidosperma cf. discolor A.DC.", 
             "Aspidosperma aff. discolor A.DC.", "Aspidosperma discolor A. & DC.", 
             "Asplenium sp. nov.", "Asplenium sp 2", 
             "Asplenium sp. nov. truncorum", "Asplenium truncorum 2", 
             "cf. Piper dilatatum", "Piper dilatatum sp. nov.")

check_status(species)
```

