---
title: "Downloading Jabot ang GBIF data from R"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{jabot}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r options, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE,
                      comment = "#>",
                      eval = TRUE)
```

Installing and loading the package:

`devtools::install_github("saramortara/rocc")`

This package also downloads records from from [GBIF](https://www.gbif.org/) and [jabot](http://jabot.jbrj.gov.br/v3/consulta.php) collections. The function `rjabot()`  makes a request to the database stored in the portal [model-r](https://model-r.jbrj.gov.br/modelr-web/). It generates the desired url and uses functions from `jsonlite` package to GET the url and save the output as a csv file. In this case, search can only be done by a species scientific name. The function `rgbif2()` encapulates funtions from **rgbif** package to receive a species scientific name and return the output as a .csv file written on disk. 

```{r setup}
#library(rocc)
devtools::load_all() # for development
```

# Using the funtion **rjabot**

## Search by species scientific name

```{r ex-01}
j01 <- rjabot(filename = "jabot-01", 
               scientificName = "Prepusa montana") 
```

```{r ex-other, eval = FALSE, echo = FALSE}
## Example 02: search by species name and province
j02 <- rjabot(filename = "jabot-02", 
              scientificName = "Prepusa Montana",
              stateProvince = "Minas Gerais")
## Example 03: search by species name and collection

j03 <- rjabot(filename = "jabot-03", 
              scientificName = "Prepusa Montana",
              stateProvince = "RB")

dim(j01$data)
dim(j02$data)
dim(j03$data)
# all examples provide the same output :facepalm:
```


# Using the funtion **rgbif2**

```{r}
g01 <- rgbif2(filename = "gbif-01",
              scientificName = "Aspidosperma limae")

dim(g01)

g02 <- rgbif2(filename = "gbif-02", 
              scientificName = "Aspidosperma melanocalyx")
dim(g02)
```

