---
title: "Geographic data download with Rocc"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Geographic data download with Rocc}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  
---

Functions `getGADM()`, `getGaz()`, and `getWDPA()` help download data from the GADM administrative units for the countries of the world [link](https://gadm.org/data.html), DIVA-GIS gazetteers (link), and the IUCN Global Database for Protected Areas ([link](https://www.iucn.org/theme/protected-areas/our-work/world-database-protected-areas)).


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::load_all()
```

```{r load}
library(dplyr)
#library(Rocc)
```

## Downloading the datasets

### GADM

Function `getGADM()` will download the GADM shapefiles in `sp` or `sf` formats if they are not already in disk. Parameter `"best = TRUE"` will seek to download the best available resolution, it will not download coarser datasets if finer resolution datasets are available. 



```{r}
countries <- c("Colombia", "Brazil", "Ecuador", "Peru", "Venezuela", "Bolivia")

iso3 <- countrycode::countrycode(countries,
                                 "country.name",
                                 "iso3c")
# Check the downloading scheme: 
df <- data.frame(codigo = rep(iso3, each = 5), pais = rep(4:0, length(countries)))
# we try the downloads at the finest scale first and ask best = TRUE to avoid downloading coarser levels. this is not beautiful, maybe the user should use EITHER level OR best internally. hmmm. if best = TRUE then default level is 4, then 3 etc. with a while loop. 
purrr::walk2(.x = rep(iso3, each = 5),
             .y = rep(4:0, length(countries)),
             ~ getGADM(
               cod = .x,
               level = .y,
               best = TRUE
             ))
```

## DIVA-GIS gazetteer

Function `getGAZ()` downloads the DIVA-GIS gazetteer files for each country. These are zipped .dbf files.

```{r}
iso3 %>% purrr::map(.x = ., ~ getGAZ(cod = .x))
```

## IUCN files

Function `getWDPA()` downloads the shapefiles from the IUCN Global Database for Protected Areas for each country. These are zipped .shp files. Read [the documentation](https://www.protectedplanet.net/en/resources/wdpa-manual) carefully, not every country has data, and it can be in different stages of completion, revision and approval. 

```{r}
iso3 %>% purrr::map(.x = ., ~getWDPA(cod = .x))
```

## 


```{r}
gadm_files <- list.files("GADM", pattern = paste(iso3, collapse = "|"), full.names = TRUE) 
lev <- stringr::str_extract(string = gadm_files, pattern = "\\d+")

gaz_files <- list.files("GAZ", pattern = ".dbf", full.names = TRUE) 

wdpa_files <- list.files("WDPA", full.names = TRUE, recursive = T, pattern = ".shp$") 
library(sf)
library(rgdal)

bol0_pts <- read_sf(wdpa_files[1])
bol0_pol <- read_sf(wdpa_files[2])
bol1_pts <- read_sf(wdpa_files[3])
bol1_pol <- read_sf(wdpa_files[4])
library(tmap)

mapbol <- tm_shape(bol) + 
  tm_polygons(col = "white") + 
  tm_shape(bol0_pol) +
  tm_fill(col = "darkgreen") + 
  tm_shape(bol1_pol) +
  tm_fill(col = "green") + 
  tm_shape(bol1_pts) + 
  tm_dots()

  
bol <- readRDS(gadm_files[1])

plot(bol[1])
maptools
library(dplyr)
bol_gaz <- read_sf(gaz_files[1]) #mk, sirve
bol_gaz <- mutate(bol_gaz, 
                  LONG = as.numeric(LONG),
                  LAT  = as.numeric(LAT)
                  ) 
coordinates(bol_gaz) <- ~LONG+LAT

ex <- head(bol_gaz)
apply(ex, 2, class)
library(sf)
st_sf(ex)

mapbol +
  tm_shape(bol_gaz) + 
  tm_dots()


```

