---
title: "Searching for species names in FB2020"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Searching for species names in FB2020}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", 
  eval = FALSE # desperate times calls for desperate measures
)
```

Package `rocc` allows the user to perform searches in the List of Species of the Brazilian Flora (FB2020) database from fields other than scientificName.

These functions download the IPT files from FB2020 to a temporary file in the computer, using package __finch__. This download can be __very slow__ the first
time and when in disk the database will access the cached files instead of downloading them.

## Function `update_flora()`

`update_flora()` will download the ipt files into folder data-raw. If a previous file exists in cache, it won't update unless `force_update = TRUE`.


Also, the function returns __all name ids irrespective of their taxonomic status__


## Function `search_flora()`

Function `search_flora()` returns lists of scientific names (in full format) for species in:

- one or more phytogeographic domains
- one or more Brazilian states
- endemics or not from Brazil

```{r library, eval = F}
library(Rocc)
```

```{r load, echo = FALSE, warning=FALSE}
devtools::load_all()
```

Here is an example of the differences between searching for species in a domain:

```{r dom}
baf <- search_flora(domain = "Mata Atlântica",
                    force_update = FALSE)
head(baf)
dim(baf)
```

```{r rj}
rj <- search_flora(stateProvince = "RJ")
head(rj)
dim(rj)
```

```{r intersect}
length(intersect(baf$id, rj$id))
```

```{r rj-and-baf}
rj_and_baf <- search_flora(domain = "Mata Atlântica",
                           stateProvince = "RJ")
head(rj_and_baf)
dim(rj_and_baf)
```


```{r not-endemic}
rj_and_baf_and_not_endemic <-
  search_flora(domain = "Mata Atlântica",
               stateProvince = "RJ",
               endemism = FALSE)
head(rj_and_baf_and_not_endemic)
dim(rj_and_baf_and_not_endemic)
```

```{r endemic}
rj_and_baf_and_endemic <-
  search_flora(domain = "Mata Atlântica",
               stateProvince = "RJ",
               endemism = TRUE)
head(rj_and_baf_and_endemic)
dim(rj_and_baf_and_endemic)
```

```{r arbusto}
rj_and_baf_and_tree <-
  search_flora(domain = "Mata Atlântica",
               stateProvince = "RJ",
               life_form = "Arbusto")
head(rj_and_baf_and_tree)
dim(rj_and_baf_and_tree)
```

```{r cda}
campos_de_altitude <-
  search_flora(domain = "Mata Atlântica",
               vegetation_type = c("campo de altitude"))
head(campos_de_altitude)
dim(campos_de_altitude)
```

```{r cdaetal}
campos_de_altitude_shrub <-
  search_flora(domain = "Mata Atlântica",
               life_form = "arbusto",
               vegetation_type = c("campo de altitude"))
head(campos_de_altitude_shrub)
dim(campos_de_altitude_shrub)
```


